Assessing glymphatic transport velocities by adjoint methods

### 2018-09-17 tex/paper.tex
Text Update

@@

\caption{ }

@@

\section{Discussion}

@@

>>>>

The first observation will be considered the initial conditions of the equation, additionally the initial conditions of the manufactured observations are not considered.  
\begin{equation}
\tau := \lbrace  0 < t  \leq 24.0\rbrace
\end{equation}
This means that the objective functional will consider one less observation. However, this can be modified by adding the initial conditions as a optimization parameter. This means the timesteps will not be the same as the manufactured solution.

This incoherence will also be investigated, and an adaptive timestep approach can be considered dependent on the results.

 Furthermore, the $g$ value will be sett equal to the next observation.

The initial values of the optimalization was set to $1000,2,1$,

@@

\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients. }

@@

\begin{table}
\centering
\caption{ }
\resizebox{\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k & $\tau$ & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
\hline
 0.1 & 1.0 &40 &10 & 743& 1187.4771691 & 4.35026181483 & 8.09946730636 \\ 
 0.1 & 0.1 &40 &10 & 932& 1555.16869771 & 6.09495269829 & 8.50884374613 \\ 
 0.1 & 0.01 &40 &10 & 1001& 3568.28083904 & 29.3015755902 & 44.1578313645 \\ 
 0.1 & 0.001 &40 &10 & 1001& 3910.1049326 & 35.4922989536 & 56.545598289 \\ 
 0.1 & 0.0001 &40 &10 & 1001& 4628.35215443 & 39.7391559549 & 63.5747349342 \\ 
 0.1 & 1e-05 &40 &10 & 1001& 4402.68260002 & 38.7772764366 & 62.3107416526 \\ 
 0.1 & 1e-06 &40 &10 & 1001& 4048.23822112 & 36.8496309935 & 58.8659971438 \\ 
 0.01 & 1.0 &40 &10 & 291& 1000.67788636 & 4.02002908826 & 7.98566981348 \\ 
 0.01 & 0.1 &40 &10 & 185& 1000.41583989 & 4.15725853533 & 8.04068211749 \\ 
 0.01 & 0.01 &40 &10 & 770& 1010.05721903 & 4.46873471103 & 8.23345999428 \\ 
 0.01 & 0.001 &40 &10 & 906& 1035.3816137 & 5.23577439946 & 8.93787811692 \\ 
 0.01 & 0.0001 &40 &10 & 933& 1054.26269562 & 5.75801399377 & 9.64500568339 \\ 
 0.01 & 1e-05 &40 &10 & 816& 1047.05756594 & 5.84828880596 & 9.82387355658 \\ 
 0.01 & 1e-06 &40 &10 & 788& 1040.16446365 & 5.75691158325 & 9.6813276929 \\ 
 0.001 & 1.0 &40 &10 & 221& 1000.18451793 & 3.98737893359 & 7.97554944332 \\ 
 0.001 & 0.1 &40 &10 & 330& 1000.32828904 & 4.04755624182 & 8.0244839499 \\ 
 0.001 & 0.01 &40 &10 & 362& 1000.3803523 & 4.11154445121 & 8.11157880655 \\ 
 0.001 & 0.001 &40 &10 & 657& 1001.71334392 & 4.19267152271 & 8.27191901359 \\ 
 0.001 & 0.0001 &40 &10 & 1001& 1004.86321852 & 4.26170953011 & 8.44356313497 \\ 
 0.001 & 1e-05 &40 &10 & 815& 1004.02931722 & 4.37346057066 & 8.57873677626 \\ 
 0.001 & 1e-06 &40 &10 & 802& 1004.22491712 & 4.37575380922 & 8.58549567766 \\ 
 0.0001 & 1.0 &40 &10 & 172& 1000.08077115 & 3.98137276814 & 7.97389541303 \\ 
 0.0001 & 0.1 &40 &10 & 284& 1000.13089398 & 4.03045319152 & 8.02261617711 \\ 
 0.0001 & 0.01 &40 &10 & 330& 1000.10285205 & 4.08364875893 & 8.09505305597 \\ 
 0.0001 & 0.001 &40 &10 & 559& 1000.5278853 & 4.10885628451 & 8.19383426091 \\ 
 0.0001 & 0.0001 &40 &10 & 342& 1000.14882303 & 4.11658048605 & 8.17742760473 \\ 
 0.0001 & 1e-05 &40 &10 & 321& 1000.08672575 & 4.05337754766 & 8.14081741343 \\ 
 0.0001 & 1e-06 &40 &10 & 551& 1000.58380151 & 4.09044639474 & 8.25619973521 \\ 
 1e-05 & 1.0 &40 &10 & 173& 1000.08653936 & 3.98154190918 & 7.97388822692 \\ 
 1e-05 & 0.1 &40 &10 & 343& 1000.20326692 & 4.03035382968 & 8.02271998911 \\ 
 1e-05 & 0.01 &40 &10 & 419& 1000.31305287 & 4.07478958493 & 8.10307012855 \\ 
 1e-05 & 0.001 &40 &10 & 437& 1000.2320762 & 4.08452785122 & 8.16938871213 \\ 
 1e-05 & 0.0001 &40 &10 & 374& 1000.11697131 & 4.07952084401 & 8.15715261877 \\ 
 1e-05 & 1e-05 &40 &10 & 463& 1000.29010188 & 4.08615998822 & 8.20191735247 \\ 
 1e-05 & 1e-06 &40 &10 & 624& 1000.69464905 & 4.08563263518 & 8.25675573539 \\ 
 1e-06 & 1.0 &40 &10 & 232& 1000.18034176 & 3.98264060176 & 7.97405892351 \\ 
 1e-06 & 0.1 &40 &10 & 287& 1000.15080505 & 4.02963675823 & 8.02269997607 \\ 
 1e-06 & 0.01 &40 &10 & 403& 1000.24828839 & 4.07422258869 & 8.09935561335 \\ 
 1e-06 & 0.001 &40 &10 & 363& 1000.16258199 & 4.10092887055 & 8.17481714787 \\ 
 1e-06 & 0.0001 &40 &10 & 413& 1000.21453049 & 4.09366239057 & 8.19045283723 \\ 
 1e-06 & 1e-05 &40 &10 & 474& 1000.34636737 & 4.09817444633 & 8.22081707472 \\ 
 1e-06 & 1e-06 &40 &10 & 475& 1000.33096416 & 4.0786358152 & 8.20801753144 \\ 
\end{tabular}}
\label{Tab::1}
\end{table}

\begin{table}
\centering
\caption{ $\tau = [1.0, 1.2, 1.4, 2.8, 4.6, 9.6, 14.4, 18.6, 22.2, 24.0] $}
\resizebox{\textwidth}{!}{\begin{tabular}{*{7}c}
$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
\hline
 0.0001 & 1.0  &20 & 352& 1005.22142783 & 3.82672281427 & 7.96012835843 \\ 
 0.0001 & 0.1  &20 & 424& 1000.74372847 & 3.48769752552 & 7.46363505824 \\ 
 0.0001 & 0.01 &20 & 709& 996.472422218 & 3.28651606815 & 6.89922591307 \\ 
 1e-05 & 1.0   &20 & 359& 1005.8332351 & 3.82683123783 & 7.96093977635 \\ 
 1e-05 & 0.1   &20 & 413& 1000.71223403 & 3.48709269446 & 7.46388730417 \\ 
 1e-05 & 0.01  &20 & 866& 995.496494833 & 3.28703772862 & 6.89839201709 \\ 
 1e-06 & 1.0   &20 & 330& 1005.36588332 & 3.82652618763 & 7.95958068842 \\ 
 1e-06 & 0.1   &20 & 390& 1000.66722857 & 3.48707900673 & 7.46307424723 \\ 
 1e-06 & 0.01  &20 & 577& 997.407662104 & 3.28668627585 & 6.90093340281 \\ 
 0.0001 & 1.0  &40 & 720& 1144.48441614 & 4.11378216282 & 8.06601345536 \\ 
 0.0001 & 0.1  &40 & 275& 1002.81529271 & 4.01476313602 & 7.99370457785 \\ 
 0.0001 & 0.01 &40 & 309& 1003.01379879 & 3.89792451751 & 7.84348036932 \\ 
 1e-05 & 1.0   &40 & 574& 1114.40281674 & 4.11652975001 & 8.06793246669 \\ 
 1e-05 & 0.1   &40 & 402& 1005.8301423 & 4.01204511666 & 7.98950535021 \\ 
 1e-05 & 0.01  &40 & 415& 1005.8339426 & 3.89483734096 & 7.83476748243 \\ 
 1e-06 & 1.0   &40 & 648& 1124.35106201 & 4.1148536647 & 8.06730484009 \\ 
 1e-06 & 0.1   &40 & 324& 1004.23408094 & 4.01236138465 & 7.99051228829 \\ 
 1e-06 & 0.01  &40 & 444& 1007.3125095 & 3.89431330176 & 7.83169391549 \\ 
\end{tabular}}
\label{Tab::1}
\end{table} 
\section{Discussion}

\begin{table}
\centering
\caption{ $\tau =[1.2, 1.4, 1.8, 2.4, 3.6, 5.4, 7.6, 17.2, 18.6, 20.4, 22.4, 24.0] $}
\resizebox{\textwidth}{!}{\begin{tabular}{*{7}c}
$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
\hline
 0.0001 & 1.0 &40 &  423& 1016.53589451 & 4.09744503422 & 8.10477831272 \\ 
 0.0001 & 0.1 &40 & 256& 1002.72187136 & 4.01772473372 & 8.01115341448 \\ 
 0.0001 & 0.01 &40& 255& 1001.77895566 & 3.940658633 & 7.89664871352 \\ 
 1e-05 & 1.0 &40  & 390& 1011.67921461 & 4.09786927743 & 8.10526579439 \\ 
 1e-05 & 0.1 &40  & 225& 1001.94506087 & 4.01805587572 & 8.01180925344 \\ 
 1e-05 & 0.01 &40 & 209& 1001.27411467 & 3.94131058751 & 7.90365080657 \\ 
 1e-06 & 1.0 &40  & 413& 1017.04677284 & 4.097319886 & 8.10398937661 \\ 
 1e-06 & 0.1 &40  & 240& 1002.43313972 & 4.01777944191 & 8.01163086184 \\ 
 1e-06 & 0.01 &40 & 356& 1003.33076616 & 3.93893764944 & 7.88611881889 \\ 
\end{tabular}}
\label{Tab::1}
\end{table} 
\section{Discussion}

 0.0001 & 1.0 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 153& 999.888464905 & 4.02189206656 & 8.01937098574 \\ 
 0.0001 & 0.1 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 82& 999.92653104 & 4.0172778853 & 8.02072488205 \\ 
 0.0001 & 0.01 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 183& 999.601435216 & 4.0167801622 & 8.02099543744 \\ 
 1e-05 & 1.0 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 170& 999.857251969 & 4.02183073053 & 8.0193786719 \\ 
 1e-05 & 0.1 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 145& 999.723425171 & 4.01725503821 & 8.02073378231 \\ 
 1e-05 & 0.01 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 189& 999.686295266 & 4.0167215691 & 8.02087841472 \\ 
 1e-06 & 1.0 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 252& 999.744572206 & 4.02186634423 & 8.01936617912 \\ 
 1e-06 & 0.1 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 167& 999.698939533 & 4.01722486087 & 8.02076770928 \\ 
 1e-06 & 0.01 &20 &[0.2, 1.2, 2.4, 3.6, 4.8, 6.0, 7.2, 8.4, 9.6, 10.8, 12.0, 13.2, 14.4, 15.6, 16.8, 17.0, 19.2, 20.4, 21.6, 22.8, 24.0] & 145& 999.76147155 & 4.01667474386 & 8.02102893936 \\

 \begin{table}
\centering
\caption{ $\tau = [2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0] $}
\resizebox{\textwidth}{!}{\begin{tabular}{*{7}c}
$\alpha$ & $\beta$ & k & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ \\
\hline
 0.001 & 1.0 &11   & 535& 1155.41620776 & 4.56890164554 & 8.74862316292 \\ 
 0.001 & 0.1 &11  & 692& 1138.18797804 & 4.77615608916 & 9.1001502642 \\ 
 0.001 & 0.01 &11 & 620& 1109.09332378 & 4.83440528908 & 9.23937192655 \\ 
 0.0001 & 1.0 &11 & 512& 1177.95965037 & 4.56118986925 & 8.74503026051 \\ 
 0.0001 & 0.1 &11 & 796& 1167.15728007 & 4.76942041977 & 9.09708917746 \\ 
 0.0001 & 0.01&11 & 726& 1147.45125238 & 4.82397769456 & 9.23132854631 \\ 
 1e-05 & 1.0 &11  & 547& 1150.09091484 & 4.56745099896 & 8.74784724393 \\ 
 1e-05 & 0.1 &11  & 774& 1209.27556281 & 4.7599962838 & 9.09240730332 \\ 
 1e-05 & 0.01 &11 & 963& 1178.62113472 & 4.81968561039 & 9.22165857548 \\ 
 1e-06 & 1.0 &11  & 516& 1178.30282045 & 4.56182347972 & 8.74408755566 \\ 
 1e-06 & 0.1 &11  & 690& 1169.85258682 & 4.76763208109 & 9.09437803203 \\ 
 1e-06 & 0.01 &11 & 885& 1161.54226173 & 4.82290410594 & 9.23253559953 \\ 
 0.001 & 1.0 &10  & 144& 1000.72690068 & 4.43617090765 & 8.47356658247 \\ 
 0.001 & 0.1 &10  & 188& 1001.11632883 & 4.42560354452 & 8.55339645884 \\ 
 0.001 & 0.01 &10 & 242& 1002.06937059 & 4.42388003439 & 8.57511846108 \\ 
 0.0001 & 1.0 &10 & 157& 1000.83218743 & 4.43452507573 & 8.47318916943 \\ 
 0.0001 & 0.1 &10 & 131& 1000.56624899 & 4.42351929725 & 8.55256760219 \\ 
 0.0001 & 0.01&10 & 174& 1001.0091989 & 4.42260942583 & 8.57478259945 \\ 
 1e-05 & 1.0 &10  & 151& 1000.79310038 & 4.43448500449 & 8.47338153139 \\ 
 1e-05 & 0.1 &10  & 140& 1000.70858373 & 4.42340629909 & 8.55312689863 \\ 
 1e-05 & 0.01 &10 & 203& 1001.34714912 & 4.42253540005 & 8.57470943099 \\ 
 1e-06 & 1.0 &10  & 115& 1000.47868283 & 4.43456295486 & 8.47226911091 \\ 
 1e-06 & 0.1 &10  & 158& 1000.8203239 & 4.42368702618 & 8.55236552474 \\ 
 1e-06 & 0.01 &10 & 142& 1000.64224198 & 4.42327990324 & 8.57047799569 \\ 
 0.001 & 1.0 &10  & 127& 1000.57534928 & 4.43620469807 & 8.47334881884 \\ 
 0.001 & 0.1 &10  & 209& 1001.40602027 & 4.42496040369 & 8.55523771434 \\ 
 0.001 & 0.01 &10 & 212& 1001.64339174 & 4.42433050528 & 8.57315746956 \\ 
 0.0001 & 1.0 &9  & 110& 999.72163906 & 4.11479310934 & 8.33462232991 \\ 
 0.0001 & 0.1 &9  & 105& 999.69280754 & 4.1045396919 & 8.33774014666 \\ 
 0.0001 & 0.01 &9 &  88& 999.772427775 & 4.10360542672 & 8.33814068545 \\ 
 1e-05 & 1.0 &9   & 129& 999.64486142 & 4.11473526399 & 8.33422818516 \\ 
 1e-05 & 0.1 &9   & 127& 999.585578036 & 4.10455462113 & 8.3375263256 \\ 
 1e-05 & 0.01 &9  &  91& 999.743943666 & 4.10325272534 & 8.33837761724 \\ 
 1e-06 & 1.0 &9   & 138& 999.565361602 & 4.11477304552 & 8.3344417303 \\ 
 1e-06 & 0.1 &9   & 127& 999.556729496 & 4.10443164325 & 8.33788684648 \\ 
 1e-06 & 0.01 &9  & 142& 999.44777782 & 4.10347962986 & 8.33800635508 \\ 
\end{tabular}}
\label{Tab::Incoherence}
\end{table} 
\section{Discussion}

The timestep incoherence between observations and Eq.\ref{Eq::PDE} was not initially considered, since the actual data do not maintain a constant timestep of the observations. However, due to the implementation this effect became apparent when the number of timesteps changed. In Tab.\ref{Tab::Incoherence} we can see that changing the number of timesteps with 1 can improve or worsen the process significantly, both parameter estimation and number of iterations. This effect mainly comes from the proximity of the observation timepoint it is.  Therefore selecting more number of timesteps than observation points seems proficient. However, using adaptive timestepping can provide means to decrease the number of iterations, but would require

The Eq.\ref{Eq::PDE} was discretized using first order Euler, thus the approximation

We can see in Fig.??, that increasing the number of timesteps will improve the estimation of diffusion coefficients.

The manufactured observations were constructed by imposing a quadratic function ?? as Dirichlet boundary conditions. Thus the number of time steps will affect the approximation of the boundary conditions

Thus

@@

The case of an observation vacancy did not show any clear discrepancy in the objective function, see Fig. ??. However, there is a divergent tendency in the estimation of $D_{\Omega_1}$, see Fig.??. This same tendency can be seen in Fig. ?? with . Although this behavior  ...

The corresponding objective function does not exhibit any discrepancy, thus the object functions dependency on $D_{\Omega_1}$ is small.

Or rather the observation function does not compute a difference. The observation function require that the parameters presence in the observations are distinct. This is not the case for cube that reach equilibrium after one timestep.

The mesh cells are of the order $\mathrm{mm}$ and the timesteps are of order $0.1$. The number of cells representing the csf is 15000.
